Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Modified the cleaning/left_joining for the retro sign up graph after moving EDGI participants to NBR

dat.retro <- dat.retro %>% 
  mutate(Sample_plot = 
           case_when(
             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
             dat.retro$Sample == "EDGI" ~ "NBR",
             dat.retro$Sample == "NBR" ~ "NBR",
             dat.retro$Sample == "RAMP" ~ "RAMP"
           ))

@@

sign_up_NBR_empty_row_April <- tibble(
  Sample_plot = "NBR",
  April = 0
)

sign_up_NBR_empty_row_August <- tibble(
  Sample_plot = "NBR",
  August = 0
)

sign_up_NBR_empty_row_September <- tibble(
  Sample_plot = "NBR",
  September = 0
)

@@

dat.retro_august_sign_up <- dat.retro_august_sign_up %>% 
  rbind(sign_up_NBR_empty_row_August)

>>>>

dat.retro <- dat.retro %>% 
  mutate(Sample_plot = 
           case_when(
             dat.retro$Sample == "GLAD" ~ "GLAD",
             dat.retro$Sample == "EDGI" ~ "NBR/EDGI",
             dat.retro$Sample == "NBR" ~ "NBR/EDGI",
             dat.retro$Sample == "RAMP" ~ "RAMP"
           ))

@@

sign_up_NBR_empty_row_April <- tibble(
  Sample_plot = "NBR/EDGI",
  April = 0
)

sign_up_NBR_empty_row_September <- tibble(
  Sample_plot = "NBR/EDGI",
  September = 0
)

@@
